Notes and code examples to accompany "If the Null Fits, You Must Omit

### 2025-12-11 index.qmd
updated docs

## Overview

@@

@@

I developed two models of experimental observations in group polarization experiments
to serve complementary purposes. First is the _expectation_ model where we model the observation of the mean

>>>>

<!-- Define the tex command for the null model -->
\newcommand{\nullmodel}{\mathcal{M}_0}

<!-- Begin main document -->
## Overview

@@

You will learn how the code works that simulates measurements of opinion change
in group polarization experiments that test if and by how much group discussion polarizes opinions. I used this modeling system to simulate 57 different group polarization experimental conditions across a corpus of ten journal articles published over several decades, and across social science subdisciplines for my paper with Paul Smaldino, "Null Fits? You Must Omit! How Measurement Artifacts Undermine Many Group Polarization Replications".

@@

I developed two models of experimental observations in group polarization experiments
to serve complementary purposes. These models provide two ways to simulate observations of _mere agreement_, which serves as our null-polarization model, $\nullmodel$,

First is the _expectation_ model where we model the observation of the average group opinion as the _expectation value_ of the distribution of ordinal opinions. We calculate the ordinal distribution of opinions by writing the endpoints of each measurement bins as limits of integration in a series of $B$ integrals, where $B$ is the number of measurement bins. For example, an example of an ordinal measurement scale might be a Likert-style series of disagree-agree levels, associated with numerical values:
-3 indicates
